---
title: "Benchmarking gibbsR and gibbsC"
author: "Hanyun Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Benchmarking gibbsR and gibbsC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp21017__ is a simple R package for the 'Statistical Computing' course. It includes two functions, namely, _gibbsR_ (R version for generating random nubers using Gibbs sampler) and _gibbsC_ (C++ version for generating random nubers using Gibbs sampler).

The R package 'microbenchmark' can be used to benchmark the above R and C++ functions.

## Benchmarking _gibbsR_ and _gibbsC_

The source R code for _gibbsR_ is as follows:
```{r,eval=FALSE}
gibbsR <- function(N, a, b, n, thin) {
  mat <- matrix(nrow = N, ncol = 2)
  x <- floor(n/2)
  y <- 0.5
  for (i in 1:N) {
    for (j in 1:thin) {
      x <- rbinom(1, size = n, prob = y)
      y <- rbeta(1, x + a, n - x + b)
    }
    mat[i, ] <- c(x, y)
  }
  mat
}
```

The above R code involves two loops, which could be very slow even for R-3.01 or any higher version. The corresponding C++ code is as follows.

```{r,eval=FALSE}
NumericMatrix gibbsC(int N, double a, double b, int n, int thin) {
  NumericMatrix mat(N, 2);
  double x = floor(n/2), y = 0.5;
  for(int i = 0; i < N; i++) {
    for(int j = 0; j < thin; j++) {
      x = rbinom(1, n, y)[0];
      y = rbeta(1, x+a, n-x+b)[0];
    }
    mat(i, 0) = x;
    mat(i, 1) = y;
  }
  return(mat);
}
```

The R code for benchmarking _gibbsR_ and _gibbsC_ is as follows.

```{r,eval=TRUE}
library(StatComp21017)
library(microbenchmark)
tm1 <- microbenchmark::microbenchmark(
  rnR = gibbsR(2000,1,4,50,10),
  rnC = gibbsC(2000,1,4,50,10)
)

knitr::kable(summary(tm1)[,c(1,3,5,6)])
```

The results again show an evident computational speed gain of C++ against R.

